On Secure Delegation of SampBQP with a Classical Client

### 2019-11-25 qpip.tex
Fix typo

	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otime n+m}$ where $\rho_i$ has over probability $\1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.

>>>>

	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.
